A model of urban evolution based on innovation diffusion

### 2020-04-30 Docs/Papers/EvolutionInnovation/paper/paper.tex
papers

@@

%%%%%%%%%%%%
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.49\linewidth]{averageDiversity-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{averageInnovation-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{averageUtility-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{finalHierarchy-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\caption{Values of indicators obtained with the grid model exploration. Each plot give each indicator among diversity $D$, utility $U$, innovation $I$ and population hierarchy $\alpha_P$, at fixed parameters $\alpha_I = 1$, $\sigma_U = 1$ and for the log-normal utility law. Indicators are plotted as a function of gravity interaction range $d_G$, for varying values of innovation diffusion range $d_I$ (color). Sub-panels show varying values of mutation rate $\beta$ (rows) and of early adoption rate $r_0$ (columns).\label{fig:exploration}}
\end{figure*}
%%%%%%%%%%%%

@@

% correlations
%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth,trim={6cm 6cm 0 6cm}]{corrmat_indics.png}
	\caption{Correlation matrix between indicators, estimated on the full grid experiment. Confidence intervals for correlations estimated with the Fisher method are tiny and not distinguishable in the plot.\label{fig:cormat}}
\end{figure}
%%%%%%%%%%%%

@@

%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{paretoDiversity-Utility_colorinnovationDecay.png}
	\caption{Pareto front for the contradictory indicator of utility and diversity obtained with the NSGA2 algorithm. Point color gives innovation interaction range $d_I$ while point size gives the number of stochastic samples.\label{fig:pareto}}
\end{figure}
%%%%%%%%%%%%

>>>>

% Urban Systems; Urban Evolution; Innovation Diffusion

@@

%%%%%%%%%%%%
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.49\linewidth]{figures/averageDiversity-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{figures/averageInnovation-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{figures/averageUtility-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\includegraphics[width=0.49\linewidth]{figures/finalHierarchy-gravityDecay_color-innovationDecay_facet-mutationRate-earlyAdoptersRate_newInnovationHierarchy1_distriblog-normal.png}
	\caption{Values of indicators obtained with the grid model exploration. Each plot give each indicator among diversity $D$, utility $U$, innovation $I$ and population hierarchy $\alpha_P$, at fixed parameters $\alpha_I = 1$, $\sigma_U = 1$ and for the log-normal utility law. Indicators are plotted as a function of gravity interaction range $d_G$, for varying values of innovation diffusion range $d_I$ (color). Sub-panels show varying values of mutation rate $\beta$ (rows) and of early adoption rate $r_0$ (columns).\label{fig:exploration}}
\end{figure*}
%%%%%%%%%%%%

@@

% correlations
%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth,trim={6cm 6cm 0 6cm}]{figures/corrmat_indics.png}
	\caption{Correlation matrix between indicators, estimated on the full grid experiment. Confidence intervals for correlations estimated with the Fisher method are tiny and not distinguishable in the plot.\label{fig:cormat}}
\end{figure}
%%%%%%%%%%%%

@@

%%%%%%%%%%%%
\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{figures/paretoDiversity-Utility_colorinnovationDecay.png}
	\caption{Pareto front for the contradictory indicator of utility and diversity obtained with the NSGA2 algorithm. Point color gives innovation interaction range $d_I$ while point size gives the number of stochastic samples.\label{fig:pareto}}
\end{figure}
%%%%%%%%%%%%
